\chapter{Introduction}
Sign language is the means of communication for deaf community with the general population. Sign language is also commonly used by the portion of the population that has hearing or speech impairments and essentially comprises of hand gestures which are used to convey any information or message. However, there are many difficulties that this portion of our population face, primarily being the fact that very few people from the hearing community know and can communicate in sign language. This fairly limits a hearing or speech impaired person who has to then use other means such as written communication or interpreters to get their message across. However written communication is slow and impersonal and the availability of translators and interpreters is also fairly low.  \\
The gap in communication for the deaf community has created a need for the development of a system that plays the role of automatic sign language recognition and translation into text. There have been many advances in computer vision and deep learning recently. There has also been significant progress in the fields of gesture recognition and motion which involve techniques that are computer vision based or deep learning based. The recent development in neural networks can be used for the implementation of sign language recognition and translation. In our proposed system, Convolution Neural Network (CNN) has been used to contribute to the field of automatic sign language recognition and translation.


\section{Problem Statement}
Difficulty for the deaf community to communicate with the general population due to the lack of understanding of sign language in the community. A significant portion of our population uses sign language to communicate, regardless, they are still faced with tremendous difficulty in their every day life in communicating.


\section{Aims and Objectives}
The aim of this project is to create and automated system for sign language recognition. The objectives have been defined as follows:  \\

\begin{itemize}
\item To recognize alphabetic and numerical hand gestures images
\item To accurately classify the alphabetic and numeric images to their meaning
\item To recognize and classify alphabetic and numeric images on a live camera feed
\end{itemize}
